### 2020-06-30 manuscript/manuscript.rmd
show software in figure

analyses_published_processed =
  analyses_published %>%
  dplyr::filter( !grepl( "Recoding", model_combined ) ) %>%
  dplyr::rename( model = model_combined ) %>%
  select( model, clade, final, inference, manuscript, matrix ) %>%
  dplyr::rename( result = final ) %>%
  mutate( status = "published" )

analyses_new_processed =
  analyses_new %>%
  mutate(model = factor(model)) %>%
  select( model, clade, result, inference, matrix ) %>%
  mutate( manuscript = NA ) %>%
  mutate( status = "new" )

analyses_processed =
  rbind( analyses_published_processed, analyses_new_processed ) %>%
  # mutate(software=recode( software, `PhyloBayes MPI`="PhyloBayes") ) %>%
  mutate(model = recode(model,
                    `GTR20` = "GTR",
                    `CAT+F81` = "Poisson+CAT",
                    `Poisson + CAT` = "Poisson+CAT",
                    `GTR + CAT` = "GTR+CAT")) %>%
  mutate(
    model = factor( model,
      levels = c("WAG", "LG", "GTR", "data partitioning",
                 "Poisson+C60", "WAG+C60", "LG+C60", "Poisson+CAT", "GTR+CAT") )) %>%
  mutate( status = factor(status, levels = c("published", "new")))

p = analyses_processed %>%
  ggplot( aes(x = model, y = clade, col = result, shape = inference) ) +
    facet_wrap( ~ status ) +
    geom_jitter( width = 0.20, height = 0.20, alpha = 0.7, size = 2 ) +
    scale_colour_manual(values = result_colors) +
    theme_classic() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
    xlab("Model") +
    ylab("Clade")

>>>>

analyses_published_processed =
  analyses_published %>%
  dplyr::filter( !grepl( "Recoding", model_combined ) ) %>%
  dplyr::rename( model = model_combined ) %>%
  select( model, clade, final, inference, manuscript, matrix, software ) %>%
  dplyr::rename( result = final ) %>%
  mutate( status = "published" )

analyses_new_processed =
  analyses_new %>%
  mutate(model = factor(model)) %>%
  select( model, clade, result, inference, matrix ) %>%
  mutate( manuscript = NA ) %>%
  mutate( status = "new" ) %>%
  mutate( software = NA )

analyses_new_processed$software[ analyses_new_processed$inference == "ML" ] = "IQTREE"

analyses_new_processed$software[ analyses_new_processed$inference == "Bayesian" ] = "PhyloBayes"

analyses_processed =
  rbind( analyses_published_processed, analyses_new_processed ) %>%
  mutate(software=recode( software, `PhyloBayes MPI`="PhyloBayes") ) %>%
  mutate(model = recode(model,
                    `GTR20` = "GTR",
                    `CAT+F81` = "Poisson+CAT",
                    `Poisson + CAT` = "Poisson+CAT",
                    `GTR + CAT` = "GTR+CAT")) %>%
  mutate(
    model = factor( model,
      levels = c("WAG", "LG", "GTR", "data partitioning",
                 "Poisson+C60", "WAG+C60", "LG+C60", "Poisson+CAT", "GTR+CAT") )) %>%
  mutate( status = factor(status, levels = c("published", "new")))

p = analyses_processed %>%
  ggplot( aes(x = model, y = clade, col = result, shape = software) ) +
    facet_wrap( ~ status ) +
    geom_jitter( width = 0.20, height = 0.20, alpha = 0.7, size = 2 ) +
    scale_colour_manual(values = result_colors) +
    theme_classic() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
    xlab("Model") +
    ylab("Clade")
